Coherent optical association of a single molecule

### 2020-10-15 paper.tex
Update on Overleaf.

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate which is a sum of all coupling sources %of $\sum_{n=i} \Gamma_e \Omega_i^2 / 4\Delta^2 $,
$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the excited molecular state, and the scattering is predominantly from the molecular state. Furthermore, the energy difference between the atomic and weakly bound state is small ($ < 1 \mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams at roughly the same single photon detuning. Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$ \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power. Thus, this results in an additional factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual states. %There are also many possible intermediate states to choose from.

>>>>

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate which is a sum of all coupling sources %of $\sum_{n=i} \Gamma_e \Omega_i^2 / 4\Delta^2 $,
$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the excited molecular state, and the scattering is predominantly from the molecular state. Furthermore, the energy difference between the atomic and weakly bound state is small ($ < 1 \mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams at roughly the same single photon detuning. Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$ \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power. Thus, this results in an additional factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual states. %There are also many possible intermediate states to choose from.
